Verifying Demonstrations

### 2018-05-23 paper/conclusions.tex
Adds comment to conclusions

Finally, most of the current methods are estimates, with quite some error 
margins. While \PRIVO is an actual count and not an estimate, its
accuracy for the total number of participants hinges on the
participants having the necessary equipment (a smartphone or similar
device), some sort of trustworthy credential, and the willingness to
run the protocol. If used today, \PRIVO would result in a
considerable undercount in most scenarios, but it presents a first
step toward accurate verifiable yet privacy-preserving crowd counting
by showing how it can be done in theory at least and in practice once
some assumptions become more realistic.

>>>>

Finally, most of the current methods are estimates, with quite some error 
margins. While \PRIVO is an actual count and not an estimate, its
accuracy for the total number of participants hinges on the
participants having the necessary equipment (a smartphone or similar
device), some sort of trustworthy credential, and the willingness to
run the protocol. If used today, \PRIVO would result in a
considerable undercount in most scenarios, \daniel{why?} but it presents a first
step toward accurate verifiable yet privacy-preserving crowd counting
by showing how it can be done in theory at least and in practice once
some assumptions become more realistic.
